\textbf{Computational Fuzzy Extractors}

### 2013-03-29 trunk/CompFuzzExt.tex
went through 3.1 and C.1 C.2

%=============================================================
\section{Impossibility of Computational Secure Sketches}
\label{sec:defCompFuzzyExtractors}
In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational entropy than information theoretic entropy.  %We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp. unpredictability) entropy when given a source with $m$ bits of entropy.  
In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the unpredictability of a sketch must decrease with the size of a ball in the metric space.  
%These results are strongest for high entropy sources.  The results get weaker as we consider sources with lower starting entropy.  If a source contains points from a good error code, then the sketch procedure does not need to output any public value so no drop occurs in entropy.

@@

Intuitively, conditional HILL entropy is as good as average min-entropy for all computationally-bounded observers.  Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.  However, as we show in Section~\ref{sec:imp HILL sketch}, such secure sketches cannot  perform much better than the information-theoretic ones.

@@

The intuition for building error-correcting codes from HILL-entropy secure sketches is as follows. Consider a function $\rec$ where $\rec (w', \sketch(w)) = w$ when $\dis(w, w')\leq t$.  When we consider the distribution $W$, to have  $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $Y$ with $\Hav(Y | \sketch(W))\geq \tilde{m}$ and $Y| \sketch(W)$ is computationally indistinguishable from $W | \sketch(W)$.  Since we know that $\rec$ succeeds with high probability, this means $\rec$ must succeed on $Y, \sketch(W)$ with high probability.  In particular, $\Pr [s\leftarrow \sketch(W) \wedge y\leftarrow Y_s\wedge y'\leftarrow B_t(y) \wedge \rec(y', s) = y ]\geq 1-\epsilon$.  This means we can construct a large set $C$ from the support of $Y$.  $C$ will be an error correcting code and $\rec$ an efficient decoder.  We can then use standard arguments to turn this code into an information theoretic sketch.  
%\lnote{this intuition is confusing, esp. given notational inconsistencies of all the capital letters with what comes above and below}
To make this intuition precise, we need an additional technical condition:  sampling a random neighbor of a point is efficient.
\begin{definition}
We say a metric space $(\mathcal{M}, \dis)$ is $(s_{sam}, t)$-\emph{neighborhood efficently-samplable} if there exists a randomized circuit $\sample$ of size $s_{sam}$ that for all $t'\leq t$, $\sample (x, t')$ outputs a random point at distance $t'$ of $x$.  
%That is $\exists \sample$ of size at most $s$ such that $\forall x\in \mathcal{M},$
%\[
%\Delta(\sample(x, t') , \{x'| \dis(x,x') = t'\})=0
%\]
\end{definition}
We require that \sample returns a point different from $x$ to ensure that each $B_t(x)$ contains at least one other point.  While we could consider metric spaces where balls only contain their center, secure sketches are not interesting in this context.

@@

We review definitions of Shannon codes~\cite{shannon1949mathematical}:
\begin{definition}
Let $\mathcal{C}$ be a set over space $\mathcal{M}$.  We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\sample(c, t')) \neq c]<\epsilon$. To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
\end{definition}
This is a slightly stronger formulation than usual, in that we require the code to correct random errors of every size $t'<t$\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compare to the volume of the ball of size $t$.  For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.  However, we work with an arbitrary recover functionality that is not necessarily monotone.}.

Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword. \begin{definition}
Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
$\Pr_{c\leftarrow C}[\rec(\sample(c, t')) \neq c]<\epsilon$.
\end{definition}
An average error Shannon code is convertible to a maximal error Shannon code with a small loss.  We use the following pruning argument from Cover and Thomas~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
\begin{lemma}
\label{lem:averageToMaximalError}
Let $C$ be a distribution over space $\mathcal{M}$ with $\Hoo(C)\geq k$ and let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$.  There is a set $C'$ with $|C'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
\end{lemma}

We can now formalize the intuition above.  A sketch that retains $\tilde{m}$-bits of HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$.  Then there exists a value $s$ and a set $C$ with $|C'|\geq 2^{\tilde{m}-2}$ that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.  If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
\end{theorem}
%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.  In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.  Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.  Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g. where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).  However, this is still a meaningful set of error correcting codes.  A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.  They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.

%It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, 
For the Hamming metric, any Shannon code (in the stronger sense defined by us) can be converted into an information-theoretic secure sketch~(see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein).  The idea is to use the code offset construction, but randomize the order of the bits of $w$ first, via  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$). The formal statement is in the following Lemma.
\begin{lemma}
\label{lem:shannon to sketch}
For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.  % with recovery procedure $\rec'$.
%  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
%
% Define the following procedures
%\lnote{I think this description is buggy}
%\begin{center}
%\begin{tabular}{c|c}
%\begin{minipage}{3in}
%\textbf{\sketch}
%\begin{enumerate}
%\item Input $w\leftarrow W$.
%\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
%\item Sample $c\leftarrow \mathcal{C}$.
%\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
%\item Output $p = x \oplus c, \pi$.
%\end{enumerate}
% \end{minipage} &
%\begin{minipage}{3in}
%\textbf{\rec}
%\begin{enumerate}
%\item Input $(w', p, \pi)$
%\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
%\item Compute $c' = p \oplus x'$.
%\item Compute $c = \rec'(c)$.
%\item Output $p\oplus c$.
%\\
%\end{enumerate}
%\end{minipage} 
%\end{tabular}
%\end{center}
Then there exists a $(Z^n, m, m-(n\log|Z|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $Z^n$. 
%satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
%\begin{itemize}
%\item Correctness: $\forall w, w'$ where $dis(w, w')\leq t$, $\Pr[\rec(w', \sketch(w))\neq w]<\epsilon$.
%\item Security: $\Hav(W |\sketch(W)) \geq \Hoo(W) - (n-\log |C|)$.
%\item Efficiency: $\sketch$ is efficient if sampling from $C$ is efficient and $\rec$ is efficient if $\rec'$ is efficient.
%\end{itemize}
\end{lemma}
%\begin{construction}
%Let $\delta >0$ be a parameter.
%Let $C$ be a $(t, \epsilon)$ Shannon code over $\{0,1\}^n$.  Choose a permutation $\pi:\mathcal{M}rightarrow \mathcal{M}$ that is $\beta$-almost independent $\ell = \delta n/\log(n)$-wise permutation.  Thefn for $\beta = 2^{-\ell}
%\end{construction}
Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
\begin{corollary}
\label{cor:rec yields sketch}
Let $Z$ be an alphabet. Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
If $s_{sec}=\Omega(t(s_{rec} + n\log |Z|))$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
$4(\epsilon+t\delta)$. 
%Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  If no $(t, \epsilon)$-average error Shannon code over $\mathcal{M}$ exists of size $2^k$ then, $\forall (s_{rec}, t)$ recovery procedures $(\sketch, \rec)$ $H^{\hill}_{\epsilon, s}(X|\sketch(X))\not\geq k$ for $s=O(s_{rec}+s_{neigh})$.
\end{corollary}
\textbf{Notes:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.

@@

\subsection{Proof of \lemref{lem:averageToMaximalError}}
\label{sec:proof of average to maximal error}
\begin{proof}
Let $C$ be a distribution with $\Hoo(C)\geq k$ and let $C$ be a  $(t,\epsilon)$-average error Shannon code with recovery procedure $\rec$.  This implies that for all $t'\le t$
\[
\sum_{c\in C} \Pr[C=c]\Pr[ c'\leftarrow \sample (c, t') \wedge \rec(c') \neq c]\leq \epsilon.
\]
For $c$ denote by $\epsilon_c = \Pr[c'\leftarrow \sample(c, t') \wedge \rec(c') \neq c]$.  
Then by Markov inequality:
\[
\Pr_{c\in C}[ \epsilon_c \leq 2\expe_{c\leftarrow C} [\epsilon_c ] ] = \Pr_{c\in C} [\epsilon_c \le 2\epsilon ] \geq \frac{1}{2}
\]
Let $C'$ denote the of  set all $c\in C$ where $\epsilon_c\leq 2\epsilon$.  Note that $\Pr_{c\leftarrow C}[c\in C']\geq 1/2$.  Since $H_\infty(C)\geq k, |C'|\geq 2^{k-1}$~(otherwise $C'$ would contain total weight less that $2^{k-1}\frac{1}{2^k} = 1/2$).  This completes the proof of the~\lemref{lem:averageToMaximalError}.

@@

\subsection{Proof of \thref{thm:impSketchArbitraryW}}
\label{sec:proof of thm sketch implies code}
\begin{proof}
  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $Y_s$ be a collection of distributions over $\mathcal{M}$ giving rise to $Y$ such that $\Hav(Y | \sketch(W))\geq k$ such that 
\[ 
\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, \sketch(W)))<\epsilon.
\]  
where  $s_{sec} = O(t(s_{neigh}+s_{rec}))$.  One such $Y$ must exist by the definition of conditional HILL entropy.
%Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$. Let $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $s=O(s_{neigh}+s_{rec})$.  This implies that $H^{\hill}_{\epsilon, s}(X|\sketch(X))\geq k$.  
Define $D$ as:
\begin{enumerate}
\item Input $z\in\mathcal{M}, s \in\{0, 1\}^*, t$.
\item For all $1\leq t'\leq t$: 
\subitem  $z'\leftarrow \sample(z, t')$.
\subitem If $\rec(z', s) \neq  z$ output $0$.
\item Output $1$.
\end{enumerate}
  By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-t\delta$.  Since 
$\delta^D((Y, \sketch(W)), (Y, \sketch(W)))<\epsilon.$ then $\Pr[D(Y, SS(W)) = 1]>1-\epsilon-t\delta$.  By Markov inequality there exists a set $S_W$ such that $\Pr[S_W]\geq 1/2$ and $\Pr[ D(Y, s) =1 | \sketch(W) = s \wedge s\in S_W]> 1- 2(\epsilon + t\delta)$.  Consider the random variable $1_{S_W}$ that is $1$ when $s\in S_X$ and otherwise.  Then,
\[
\Hav(Y  | W) = -\log \left( \Pr[W\in 1_{S_W}] 2^{-\Hav(Y | W\in 1_{S_W})} + \Pr[W\not\in 1_{S_W}] 2^{-\Hav (Y|W\not\in 1_{S_W})} \right)
\] 
Rearranging terms:
\begin{align*}
\Pr[W\in 1_{S_W}] 2^{-\Hav(Y | W\in 1_{S_W})} &= 2^{-\Hav(Y  | W) } - \Pr[W\not\in 1_{S_W}] 2^{-\Hav (Y|W\not\in 1_{S_W})}\\
&=2^{-\Hav(Y  | W) } = 2^{-k}
\end{align*}
This means that $2^{-\Hav(Y | W\in 1_{S_W})} \geq 2^{-k}/\Pr[W\in 1_{S_W}] = 2^{-k+1}$.  That is, $\Hav(Y|W\in 1_{S_W})\geq k-1$.  Fix one value $s \in 1_{S_W}$ such that $\Hav(Y | s)\geq k-1$.
%This means at least one $x'$ where this equation holds.  Fix one such $x'$.  
%This implies that $D(W, \sketch(x'))\geq 1-\epsilon$.  
Thus, for all $t', 1\leq t'\leq t$ on a random $y$
\[ \Pr_{y\leftarrow Y_s}[y'\leftarrow \sample(y, t') \wedge \rec(y',s) = y]\geq 1-2(\epsilon+t\delta).\]  
%Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
Thus,  $Y$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,s)$.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
\end{proof}

>>>>

%=============================================================
\section{Impossibility of Computational Secure Sketches}
\label{sec:defCompFuzzyExtractors}
In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational entropy than information theoretic entropy.  %We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp. unpredictability) entropy when given a source with $m$ bits of entropy.  
In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the unpredictability of a sketch must decrease with the size of a ball in the metric space \lnote{not the most clear sentence}.  
%These results are strongest for high entropy sources.  The results get weaker as we consider sources with lower starting entropy.  If a source contains points from a good error code, then the sketch procedure does not need to output any public value so no drop occurs in entropy.

@@

\lnote{is there any reason we can't work for the more relaxed notion of HILL, where the condition can be changed, too?}Intuitively, conditional HILL entropy is as good as average min-entropy for all computationally-bounded observers.  Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.  However, as we show in Section~\ref{sec:imp HILL sketch}, such secure sketches cannot  perform much better than the information-theoretic ones. \lnote{this paragraph needs rephrasing and better gluing with the next one}

@@

The intuition for building error-correcting codes from HILL-entropy secure sketches is as follows.  In order to have  $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $Y$ such that $\Hav(Y | \sketch(W))\geq \tilde{m}$ and $(Y, \sketch(W))$ is computationally indistinguishable from $(W, \sketch(W))$.  Sample a sketch $s\leftarrow \sketch(W)$. We know that $\sketch$ followed by $\rec$ likely succeeds on $W|s$  (i.e., $\rec (w', s) = w$ with high probability for $w\leftarrow W|s$ and $w'\leftarrow B_t(w)$).  So, by indistinguishability, it must also succeed on $Y$: specifically, $\rec (y',s) = y$ with high probability, for $y\leftarrow Y|s$ and $y'\leftarrow B_t(y)$).
 This means we can construct a large set $C$ from the support of $Y|s$.  $C$ will be an error correcting code and $\rec$ an efficient decoder.  We can then use standard arguments to turn this code into an information theoretic sketch.

To make this intuition precise, we need an additional technical condition:  sampling a random neighbor of a point is efficient.
\begin{definition}
We say a metric space $(\mathcal{M}, \dis)$ is $(s_{sam}, t)$-\emph{neighborhood efficently-samplable} if there exists a randomized circuit $\sample$ of size $s_{sam}$ that for all $t'\leq t$, $\sample (x, t')$ outputs a random point at distance $t'$ of $x$.  
%That is $\exists \sample$ of size at most $s$ such that $\forall x\in \mathcal{M},$
%\[
%\Delta(\sample(x, t') , \{x'| \dis(x,x') = t'\})=0
%\]
\end{definition}
We require that \sample returns a point different from $x$ to ensure that each $B_t(x)$ contains at least one other point.  While we could consider metric spaces where balls only contain their center, secure sketches are not interesting in this context. \lnote{ do we need this? if distance is exactly $t'$, then the point is different as long as $t'>0$.  So why not just say "exactly $t'$ in the definition?}

@@

We review definitions of Shannon codes~\cite{shannon1949mathematical}:
\begin{definition}
\label{def:shannon-code}
Let $\mathcal{C}$ be a set over space $\mathcal{M}$.  We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\sample(c, t')) \neq c]<\epsilon$. To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
\end{definition}
This is a slightly stronger formulation than usual, in that we require the code to correct random errors of every size $t'<t$\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compare to the volume of the ball of size $t$.  For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.  However, we work with an arbitrary recover functionality that is not necessarily monotone.}.

Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword. \lnote{is there a source we can reference for the terms average-error and maximal-error?}

 \begin{definition}
Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
$\Pr_{c\leftarrow C}[\rec(\sample(c, t')) \neq c]<\epsilon$.
\end{definition}
An average-error Shannon code is convertible to a maximal-error Shannon code with a small loss.  We use the following pruning argument from Cover and Thomas~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
\begin{lemma}
\label{lem:averageToMaximalError}
Let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$ such that $\Hoo(C)\geq k$.  There is a set $C'$ with $|C'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
\end{lemma}

We can now formalize the intuition above.  A sketch that retains $\tilde{m}$-bits of HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood \lnote{why $s_{neigh}$ and not $s_{sam}$ as above?} samplable.  Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$ \lnote{I don't think the asymptotics work here -- we are using concrete parameters, nothing is going to $\infty$, so what does $\Omega$ mean?} .  Then there exists a value $s$ and a set $C$ with $|C|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.  If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
\end{theorem}
%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.  In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.  Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.  Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g. where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).  However, this is still a meaningful set of error correcting codes.  A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.  They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.

%It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, 
For the Hamming metric, any Shannon code (as defined in Definition~\ref{def:shannon-code}) can be converted into an information-theoretic secure sketch~(as described in \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein).  The idea is to use the code offset construction, and convert worst-case errors to random errors by randomizing the order of the bits of $w$ first, via a randomly chosen  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$). The formal statement is in the following Lemma.
\begin{lemma}
\label{lem:shannon to sketch}
For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.  % with recovery procedure $\rec'$.
%  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
%
% Define the following procedures
%\lnote{I think this description is buggy}
%\begin{center}
%\begin{tabular}{c|c}
%\begin{minipage}{3in}
%\textbf{\sketch}
%\begin{enumerate}
%\item Input $w\leftarrow W$.
%\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
%\item Sample $c\leftarrow \mathcal{C}$.
%\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
%\item Output $p = x \oplus c, \pi$.
%\end{enumerate}
% \end{minipage} &
%\begin{minipage}{3in}
%\textbf{\rec}
%\begin{enumerate}
%\item Input $(w', p, \pi)$
%\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
%\item Compute $c' = p \oplus x'$.
%\item Compute $c = \rec'(c)$.
%\item Output $p\oplus c$.
%\\
%\end{enumerate}
%\end{minipage} 
%\end{tabular}
%\end{center}
Then there exists a $(Z^n, m, m-(n\log|Z|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $Z^n$. 
%satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
%\begin{itemize}
%\item Correctness: $\forall w, w'$ where $dis(w, w')\leq t$, $\Pr[\rec(w', \sketch(w))\neq w]<\epsilon$.
%\item Security: $\Hav(W |\sketch(W)) \geq \Hoo(W) - (n-\log |C|)$.
%\item Efficiency: $\sketch$ is efficient if sampling from $C$ is efficient and $\rec$ is efficient if $\rec'$ is efficient.
%\end{itemize}
\end{lemma}
%\begin{construction}
%Let $\delta >0$ be a parameter.
%Let $C$ be a $(t, \epsilon)$ Shannon code over $\{0,1\}^n$.  Choose a permutation $\pi:\mathcal{M}rightarrow \mathcal{M}$ that is $\beta$-almost independent $\ell = \delta n/\log(n)$-wise permutation.  Thefn for $\beta = 2^{-\ell}
%\end{construction}
Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
\begin{corollary}
\label{cor:rec yields sketch}
Let $Z$ be an alphabet. Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
If $s_{sec}=\Omega(t(s_{rec} + n\log |Z|))$ \lnote{same comment about $\Omega$}, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
$4(\epsilon+t\delta)$. 
%Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  If no $(t, \epsilon)$-average error Shannon code over $\mathcal{M}$ exists of size $2^k$ then, $\forall (s_{rec}, t)$ recovery procedures $(\sketch, \rec)$ $H^{\hill}_{\epsilon, s}(X|\sketch(X))\not\geq k$ for $s=O(s_{rec}+s_{neigh})$.
\end{corollary}
\textbf{Notes:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.

@@

\subsection{Proof of \lemref{lem:averageToMaximalError}}
\label{sec:proof of average to maximal error}
\begin{proof}
Let $C$ be the  $(t,\epsilon)$-average error Shannon code with recovery procedure $\rec$ such that  $\Hoo(C)\geq k$.  Then for all $t'\le t$
\[
\sum_{c\in C} \Pr[C=c]\Pr[ c'\leftarrow \sample (c, t') \wedge \rec(c') \neq c]\leq \epsilon.
\]
For $c$ denote by $\epsilon_c = \Pr[c'\leftarrow \sample(c, t') \wedge \rec(c') \neq c]$.  
Then by Markov's inequality:
\[
\Pr_{c\in C}[ \epsilon_c \leq 2\expe_{c\leftarrow C} [\epsilon_c ] ] = \Pr_{c\in C} [\epsilon_c \le 2\epsilon ] \geq \frac{1}{2}
\]
Let $C'$ denote the of  set all $c\in C$ where $\epsilon_c\leq 2\epsilon$.  Note that $\Pr_{c\leftarrow C}[c\in C']\geq 1/2$.  Since $H_\infty(C)\geq k$, we know $|C'|\geq 2^{k-1}$~(otherwise $\Pr_{c\leftarrow C}[c\in C']=\sum_{c\in C'}\Pr[C=c]$ would be less than $2^{k-1}\frac{1}{2^k} = 1/2$).  This completes the proof of the~\lemref{lem:averageToMaximalError}.

@@

\subsection{Proof of \thref{thm:impSketchArbitraryW}}
\label{sec:proof of thm sketch implies code}
\begin{proof}
  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $Y_s$ be a collection of distributions over $\mathcal{M}$ giving rise to $Y$ such that $\Hav(Y | \sketch(W))\geq k$ and
\[ 
\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, \sketch(W)))<\epsilon.
\]  
where  $s_{sec} = O(t(s_{neigh}+s_{rec}))$\lnote{again, why asysmptotics?}.  One such $Y$ must exist by the definition of conditional HILL entropy.
%Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$. Let $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $s=O(s_{neigh}+s_{rec})$.  This implies that $H^{\hill}_{\epsilon, s}(X|\sketch(X))\geq k$.  
Define $D$ as:
\begin{enumerate}
\item Input $z\in\mathcal{M}, s \in\{0, 1\}^*, t$.
\item For all $1\leq t'\leq t$: 
\subitem  $z'\leftarrow \sample(z, t')$.
\subitem If $\rec(z', s) \neq  z$ output $0$.
\item Output $1$.
\end{enumerate}
 By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-t\delta$.  Since 
$\delta^D((Y, \sketch(W)), (Y, \sketch(W)))<\epsilon$, we know $\Pr[D(Y, \sketch(W)) = 1]>1-\epsilon-t\delta$.  By Markov's inequality,  there exists a set $S_W$ such that $\Pr[\sketch(W)\in S_W]\ge 1/2$ and for all $s\in \sketch(W)$, $\Pr[ D(Y_s, s) =1]> 1- 2(\epsilon + t\delta)$.  Moreover, by \cite[Lemma 2.2a]{DBLP:journals/siamcomp/DodisORS08} (which is derived simply via Markov's inequality applied to the positive random variable $\max_y \Pr[Y_s=y]$), there exists a set $S'_W$ such that $\Pr[\sketch(W)\in S'_W]> 1/2$ and for all $s\in \sketch(W)$, $\Hoo(Y_s)\ge k-1$. \lnote{simplified this derivation}  Fix one value $s \in S_W\cap S'_W$ (which exists because the sum of probabilities of $S_W$ and $S'_W$ is greater than 1).  
Thus, for all such that $t', 1\leq t'\leq t$, 
\[ \Pr_{y\leftarrow Y_s}[y'\leftarrow \sample(y, t') \wedge \rec(y',s) = y]> 1-2(\epsilon+t\delta).\]  
%Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
Thus,  $Y$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,s)$.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
\end{proof}
